DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-06 paper/comparison.tex
Add TX2 discussion/results to comparison
Also made some minor changes.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/system_multicore}
  \caption{Inferencing time across platforms based on number of cores used.}
  \label{fig:sys_core}
\end{figure}

The results of the multicore tests can be seen in Figure~\ref{fig:sys_core}. It was found that the 
Intel UP Board performed better in all experiments. On average, it was able to perform inferencing 
operations, at least, twice as fast as the Raspberry Pi 3. As a result, the UP Board was able to 
satisfy the 50 ms WCET by a very clear margin (in the worst case, it would still meet it by $\sim$20 
ms), and, thus, demonstrates that it is more capable of autonomous driving than the Raspberry Pi 3.

The Intel UP Board also performed better in the multimodel tests, as is shown in 
Figure~\ref{fig:sys_model}. Once again, the UP was able to complete inferecing operations in half the 
time when compared to the Pi. Furthermore, the Intel UP Board was capable of satisfying the 50 ms 
WCET, while the Raspberry Pi 3 was unable to do so. As such, the Intel UP Board displays greater 
potential for the simultaneous execution of multiple models during self-driving operation, while the 
Raspberry Pi 3 would struggle to do so.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/system_multimodel}
  \caption{Inferencing time across platforms based on number of models run concurrently.}
  \label{fig:sys_model}
\end{figure}

Finally, we examined if the performance of the Intel UP Board and Tegra TX2 would be affected by the 
addition of the synthetic benchmarks. As summarized in Figure~\ref{fig;sys_bench}, the Intel UP Board 
did experience a change in its inferencing times, but the increase was not as drastic as is seen by 
the Raspberry Pi 3. in the worst case, the Intel UP Board produced times that were over two times as 
large, whereas the Raspberry Pi 3 output times that were around 10 times greater. The Intel UP Board 
was successful in completing inferencing operations in under 50 ms when benchmarks were run on a 
maximum of 2 cores, while the Raspberry Pi 3 failed to do so when any benchmark was introduced. As 
such, it can be concluded that the Intel UP Board would be more capable of running computationally 
heavy processes during autonomous driving, and that the Pi wouldn't be able to do the same.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/system_benchmark}
  \caption{Inferencing time across platforms based on number of cores used.}
  \label{fig:sys_bench}
\end{figure}

In the comparison of the real-time capabilities of three embedded computing platforms, we found that 
the Raspberry Pi 3 performed the worst. When compared to the Intel UP Board, inferencing on the Pi 
took twice as long across all multicore and multimodel experiments. The difference was even more 
noticeable in the the addition of computationally heavy synthetic benchmarks that had a much more 
dire effect on the Pi.

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_core}
  \caption{Inferencing time across platforms based on number of cores 
used.}
  \label{fig:sys_core}
\end{figure}

The results of the multicore tests can be seen in 
Figure~\ref{fig:sys_core}. It was found that the both the Tegra TX2 
and the Intel UP Board performed better than the Raspberry Pi 3 in 
all experiments. On average, the UP was able to perform inferencing 
operations, at least, twice as fast as the Raspberry Pi 3. The 
difference was even greater with the TX2, as control loops, in the 
worst case, were 3x faster using only the CPU and 10x quicker when 
using the GPU. As a result, they were all able to satisfy the 50 ms 
WCET by a very clear margin (in the worst case, the UP Board would 
still meet it by $\sim$20 ms), and, thus, demonstrates that they are 
more capable of autonomous driving than the Raspberry Pi 3.

The UP Board and TX2 also performed better in the multimodel tests, 
as is shown in Figure~\ref{fig:sys_model}. Once again, they were able 
to complete control loops in a fraction of the time when compared to 
the Pi. Furthermore, both of the platforms satisfied the 50 ms WCET 
in all experiments, while the Raspberry Pi 3 was unable to do so. As 
such, the UP Board and TX2 display greater potential for the 
simultaneous execution of multiple models during self-driving 
operation, while the Raspberry Pi 3 would struggle to do so.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_model}
  \caption{Inferencing time across platforms based on number of 
models run concurrently.}
  \label{fig:sys_model}
\end{figure}

Finally, we examined if the performance of the Intel UP Board and 
Tegra TX2 would be affected by the addition of the synthetic 
benchmarks. As summarized in Figure~\ref{fig;sys_bench}, the both 
experienced a change in their inferencing times, but the increases 
were not as drastic as is seen by the Raspberry Pi 3. in the worst 
case, both the UP Board and TX2 (CPU only and GPU) produced times 
that were over two times as large, whereas the Raspberry Pi 3 output 
times that were around 10 times greater. The Intel UP Board was 
successful in completing inferencing operations in under 50 ms when 
benchmarks were run on a maximum of 2 cores, and the TX2 was 
successful in all experiments irrespective of the computing resources 
utilized. Comparetively, both performed better than the Raspberry Pi 
3 which failed to meet its deadlines when any benchmark was 
introduced. As such, it can be concluded that the Intel UP Board 
would be more capable of running computationally heavy processes 
during autonomous driving, and that the Pi wouldn't be able to do the 
same.

\begin{figure}[h]
  \centering
  \includegraphics[width=.5\textwidth]{figs/compare_benchmark}
  \caption{Inferencing time across platforms based on number of cores 
used.}
  \label{fig:sys_bench}
\end{figure}

In the comparison of the real-time capabilities of three embedded 
computing platforms, we found that the Raspberry Pi 3 performed the 
worst. When compared to the Intel UP Board and the NVIDIA Tegra TX2, 
control loops on the Pi were shown to take noticably longer to 
complete, regardless of the number of cores utilized or the number of 
neural network models run simultaneoulsy. The difference was even 
more noticeable in the the addition of computationally heavy 
synthetic benchmarks that had a much more dire effect on the Pi. In 
the worst case, an average control loop on the Pi took an abnormally 
long amount of time to finish. Compared to the TX2 with GPU support, 
those times were 34.8X times greater. From this, we find that the UP 
Board and Tegra TX2 are superior platforms for real-time CNN 
operations. However, due to the Pi's ability to satisfy the 50 ms 
WCET in some experiments, we conclude that the Raspberry Pi 3 is 
feasible for autonomous research.
